Solar wind and geomagnetic activity influence on the equatorial plasma mass density at geosynchronous orbit

### 2016-08-17 paper/paper.tex
Abstract update

%\twocolumn[
%  \begin{@twocolumnfalse}
%\maketitle
%\hrule
\begin{abstract}
We consider two types of events, identified by decreases in $D_{st}$ below a threshold value and increases in the the equatorial mass density at geosynchronous altitudes, $\rho_{eq}$, above a threshold value using the \cite{Takahashi2010} dataset.  From the $D_{st}$ events and 1-day averages, we find that there is a statistically weak and small amplitude difference between $\rho_{eq}$ on the day of the event and the days before and after.  For hourly averages, it is found that for 6 hours after onset, very few measurements of $\rho_{eq}$ exist and that most of the contribution to the daily averages is from 6-24 hours after onset.  For hourly averages, $\rho_{eq}$ following the onset of a $D_{st}$ event does not depend on the north-south component of the interplanetary magnetic field, $B_z$ near onset time. The primary factor that determines if a post-$D_{st}$ event onset peak in $\rho_{eq}$ will occur in the hourly averages is elevated $F10.7$.  From the $\rho_{eq}$ events, we find a weak dependence on $B_{z}$ after the onset of an event, with higher average $B_{z}$ four hours after the event onset corresponding to larger $\rho_{eq}$ values 24-36 hours after onset.  In contrast, the average of $B_z$ four hours prior to $\rho_{eq}$ events does not have a statistically significant impact on $\rho_{eq}$ after onset.
\end{abstract}
%\vspace{2em}
%\hrule
%\vspace{2em}
% \end{@twocolumnfalse}
%  ]

>>>>

%\twocolumn[
%  \begin{@twocolumnfalse}
%\maketitle
%\hrule
\begin{abstract}
We consider two types of events, identified by decreases in $D_{st}$ below a threshold value and increases in the the equatorial mass density at geosynchronous altitudes, $\rho_{eq}$, above a threshold value using the \cite{Takahashi2010} dataset.  From the $D_{st}$ events and 1-day averages, we find that there is a statistically weak and small-amplitude difference between $\rho_{eq}$ on the day of the event and the days before and after.

For hourly averages, $\rho_{eq}$ following the onset of a $D_{st}$ event does not depend on the north-south component of the interplanetary magnetic field, $B_z$ near onset time. The primary factor that determines the post-$D_{st}$ event onset peak amplitude in $\rho_{eq}$ in the hourly averages is elevated $F10.7$.  From the $\rho_{eq}$ events, we find a weak dependence on $B_{z}$ after the onset of an event, with higher average $B_{z}$ four hours after the event onset corresponding to larger $\rho_{eq}$ values 24-36 hours after onset.  In contrast, the average of $B_z$ four hours prior to $\rho_{eq}$ events does not have a statistically significant impact on $\rho_{eq}$ after onset.
\end{abstract}
%\vspace{2em}
%\hrule
%\vspace{2em}
% \end{@twocolumnfalse}
%  ]
